\Title

### 2023-02-09 Grimaldi-etal-BiolCybernetics.tex
Methods : 3

From the perspective of simulating such event-based computations on standard CPU- or GPU-based computers and then using parallel computing, it is useful to transform this event-based representation into a dense representation. Indeed, by discretization of time, we may transform any event-based input as the boolean matrix $A \in \{0, 1 \}^{N\times T}$, where $N$ is the number of neurons in $\presynaddrspace$ and $T$ is the number of time bins. In this simplified model, we will consider that heterogeneous delays are limited in range such that the synaptic set can be represented by the dense matrix $\kernel^\postsynaddr$ of size $(\Ntime, \Nx, \Ny)$, where $\Ntime$ is the number of time bins, $\Nx$ and $\Ny$ are the number of pixels in both spatial dimensions. For each neuron $\postsynaddr$, $\kernel^\postsynaddr$ gives the weights as a function of presynaptic address and delay: $\forall {\ranksyn \in \synapse^\postsynaddr}, \kernel^\postsynaddr(\presynaddr_\ranksyn, \synapticdelay_\ranksyn) = \synapticweight_\ranksyn$. Therefore, if we make the approximation that one neuron integrates only on the temporal window given by its variety of synaptic delays, the integration of the spike train as input can be formalized by a 3D convolution operation. The longest synaptic delay defines the depth of the kernel $\kernel^\postsynaddr$ and all possible delays associated to the different presynaptic addresses are represented. Using this dense representation, the integration of the spike train as input by the synapses of neuron $\postsynaddr$ is:

@@

Since the model is fully differentiable, we can now implement a semi-supervised learning rule. The loss function of the MLR model is the binary cross-entropy on the output of the classification layer. Supervision was implemented using the input binary events as defined above and the motion direction labels as the desired output. The labels were defined at each time point as a one-shot encoding of the current motion in the channel corresponding to the current motion for all positions. As in this semi-supervised context, the label is known, but the timing is not, we used a selection of the temporal support in an unsupervised manner. It is important to note that we weighted the cost function by considering only active cells, such that the error is only back propagated to the spatial locations of these most active cells. This is reminiscent of previous methods solving this problem using a Winner-Takes-All mechanism~\citep{masquelier_unsupervised_2007}. Simulations are performed with the PyTorch library using gradient descent with Adam (for $2^{12}$ movies and a learning rate of $10^{-5}$). We demonstrated in a previous work that this type of learning algorithm can be assimilated to a Hebbian learning mechanism~\cite{grimaldi_robust_2022}.  

>>>>

From the perspective of simulating such event-based computations on standard CPU- or GPU-based computers and then using parallel computing, it is useful to transform this event-based representation into a dense representation. Indeed, by discretization of time, we may transform any event-based input as the boolean matrix $A \in \{0, 1 \}^{N\times T}$, where $N$ is the number of neurons in $\presynaddrspace$ and $T$ is the number of time bins. In this simplified model, we will consider that heterogeneous delays are limited in range such that the synaptic set can be represented as a kernel by the dense matrix $\kernel^\postsynaddr$ of size $(\Ntime, \Nx, \Ny)$, where $\Ntime$ is the number of delays and $\Nx$ and $\Ny$ are the number of pixels in both spatial dimensions. For each neuron $\postsynaddr$, $\kernel^\postsynaddr$ gives the weights as a function of presynaptic address and delay: $\forall {\ranksyn \in \synapse^\postsynaddr}, \kernel^\postsynaddr(\presynaddr_\ranksyn, \synapticdelay_\ranksyn) = \synapticweight_\ranksyn$. Therefore, if we make the approximation that one neuron integrates only on the temporal window given by its variety of synaptic delays, the integration of the spike train as input can be formalized by a 3D convolution operation. The longest synaptic delay defines the depth of the kernel $\kernel^\postsynaddr$ and all possible delays associated to the different presynaptic addresses are represented. Using this dense representation, the integration of the spike train as input by the synapses of neuron $\postsynaddr$ is:

@@

Since the model is fully differentiable, we can now implement a semi-supervised learning rule. The loss function of the MLR model is the binary cross-entropy on the output of the classification layer. Supervision was implemented using the input binary events as defined above and the motion direction labels as the desired output. The labels were defined at each time point as a one-hot encoding of the current motion in the channel corresponding to the current motion for all positions. As in this semi-supervised context, the label is known, but the timing is not, we used a selection of the temporal support in an unsupervised manner. It is important to note that we weighted the cost function by considering only active cells, such that the error is only back propagated to the spatial locations of these most active cells. This is reminiscent of previous methods solving this problem using a Winner-Takes-All mechanism~\citep{masquelier_unsupervised_2007}. Simulations are performed with the PyTorch library using gradient descent with Adam (for $2^{12}$ movies and a learning rate of $10^{-5}$). We demonstrated in a previous work that this type of learning algorithm can be assimilated to a Hebbian learning mechanism~\cite{grimaldi_robust_2022}.  
